Manuscript

### 2022-11-15 analysis/manuscript.Rmd
save figures as pdf

```{r setup, include = FALSE, dev=c('png', 'pdf')}

@@

knitr::opts_chunk$set(dev =c('png', 'pdf'))

@@

pearson_vs_spearman_plot
```

@@

  theme_minimal() +

  #geom_text(aes(x=1,y=2,label=""),show.legend=F) +
  ggplot2::labs(x = paste0("Male place of birth (NC)"),
                y = paste("Female place of birth (NC)")) + 
  geom_smooth(method=lm , color="red", fill="#69b3a2", se=TRUE) +
  theme_ipsum()

@@

@@

@@

@@

@@

@@

figures_grid <- plot_grid(plotlist = plots, nrow=2, ncol = 2, byrow = F, labels="AUTO")
figures_grid
```

@@

@@

  coord_cartesian(ylim=c(-0.5, 0.75)) +
  scale_fill_viridis(discrete = TRUE, alpha=0.6, option="A") +
  theme_ipsum() +
  theme(
    legend.position="none",
    plot.title = element_text(size=11)
  ) +
  #labs(x ="Estimate", y = "") +
  scale_x_discrete(labels=c("Omega" = "\u03C9", 
                            "Gamma" = "\u03B3", "Gamma_Rho_resid" = expression( paste(rho ["resid"], " + ", gamma)), "Rho" = "\u03C1")) +
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank())

@@

>>>>

```{r setup, include = FALSE}

@@

#knitr::opts_chunk$set(dev =c('png', 'pdf'))

@@

pearson_vs_spearman_plot
ggsave("docs/figure/manuscript.Rmd/pearson_vs_spearman_plot.pdf", pearson_vs_spearman_plot, device = cairo_pdf)

@@

  #theme_minimal() +

  #geom_text(aes(x=1,y=2,label=""),show.legend=F) +
  ggplot2::labs(x = paste0("Male place of birth (NC)"),
                y = paste("Female place of birth (NC)")) + 
  geom_smooth(method=lm , color="red", fill="#69b3a2", se=TRUE) +
  theme_ipsum_rc()

@@

ggsave("docs/figure/manuscript.Rmd/pheno_corr_plot.pdf", pheno_corr_plot, device = cairo_pdf)

@@

ggsave("docs/figure/manuscript.Rmd/corr_vs_MR_effects_plot.pdf", corr_vs_MR_effects_plot, device = cairo_pdf)

@@

ggsave("docs/figure/manuscript.Rmd/summ_C_plot.pdf", summ_C_plot, device = cairo_pdf)

@@

ggsave("docs/figure/manuscript.Rmd/corr_vs_MR_comb.pdf", corr_vs_MR_comb, device = cairo_pdf)

@@

ggsave("docs/figure/manuscript.Rmd/pheno_binned_figures.pdf", pheno_binned_figures, device = cairo_pdf)

@@

figures_grid <- plot_grid(plotlist = plots, nrow=2, ncol = 2, byrow = F, labels="AUTO")
figures_grid

@@

ggsave("docs/figure/manuscript.Rmd/causal_confounder_plot.pdf", figures_grid, device = cairo_pdf)

@@

  coord_cartesian(ylim=c(-0.5, 0.75)) +
  scale_fill_viridis(discrete = TRUE, alpha=0.6, option="A") +
  theme_ipsum_rc() +
  theme(
    legend.position="none",
    plot.title = element_text(size=11)
  ) +
  #labs(x ="Estimate", y = "") +
  scale_x_discrete(labels=c("Omega" = "\u03C9", 
                            "Gamma" = "\u03B3", "Gamma_Rho_resid" = expression( paste(rho ["resid"], " + ", gamma)), "Rho" = "\u03C1")) +
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank())

@@

ggsave("docs/figure/manuscript.Rmd/boxplot_combined.pdf", figures_grid, device = cairo_pdf)
